---
title: "W21-Final"
author: "Richard Ye"
date: "2023-04-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Q3

## Part A

Finding kelly criterion based on EVaR
```{r}
EVaR_opt = function(x){
  return( (2+1/x)*log(1+2*x)-(1/x-1)*log(1-x)-1)
  }

f_ = optimize(EVaR_opt, c(0,1), maximum=T)$maximum
f_
```

## Part B
Simulate 1000 wealth paths consisting of 30 investments steps each using the Kelly fraction from the previous part (or, if you didn’t get it, just f = .7). On the same axes, plot the mean simulated wealth, and the 5% and 95% quantiles of the simulated wealth at each step.

```{r}
set.seed(123)
n=1000; m=30
r_i = runif(n*m, -1, 2) %>% matrix(nrow=n,ncol=m)

# 1+f_*r_i is the amount of wealth at time i after betting f_ of wealth

# applies the function cumprod over columns for each row, where every value has 
# been augmented to 1+f_*r_i
V = apply(1+f_*r_i, 1, cumprod)

#Avg value of each path
V_avg = apply(V, 1, mean)
V_95 = apply(V, 1, quantile, prob=.95)
V_05 = apply(V, 1, quantile, prob=.05)

plot( V_avg, type = "l", ylim = c(.001,10000) )
lines( V_05, col=2 ); lines( V_95, col = 2 )

plot( V_avg, type = "l", log="y", ylim = c(.001,25000) )
lines( V_05, col=2 ); lines( V_95, col = 2 )
```

## Part C

In class, we mentioned that the Kelly criterion strategy reaches any wealth level faster than other strategies. You will test this claim with a simulation experiment. Fix a target wealth of 10,000 and simulate 1,000 paths with as many steps necessary to reach or exceed this level, under both the Kelly strategy (f∗) and the all-in strategy (f = 1). Report the average number of steps required to reach or exceed the target wealth under each strategy. Does it confirm the claim?

```{r}
targ = 10000
T_kelly = T_allin = integer(1000)

set.seed(123)
for(i in 1:1000){
  #kelly
  V = 1; j = 0
  while(V<targ){
    V = V * ( 1+f_*runif(1,-1,2) )
    j = j + 1
  }
  T_kelly[i] = j
  #all-in
  V = 1; j = 0
  while(V<targ){
    V = V * ( 1+ runif(1,-1,2) )
    j = j + 1
  }
  T_allin[i] = j
}

mean(T_kelly)
mean(T_allin)
```

# Q4

## Part A

```{r}
load("STAD70_W21_Final.RData")
b = model.matrix( object = ~ sectors - 1 )
f = matrix( 0, nrow = nrow(R), ncol = nlevels(sectors) )
e = matrix(0, nrow = nrow(R), ncol = ncol(R) )
for( i in 1:nrow(R) ){
tmp = lm( R[i,] ~ b - 1 )
f[i,] = tmp$coefficients
e[i,] = tmp$residuals
}
```

```{r}
plot(f[,1], f[,2])
```

## Part B
```{r}
v = var(R)
sig_inv = solve(v)
weights = rowSums(sig_inv) / sum(sig_inv)
weights
```

## Part C
Use the industry factor model to estimate the return covariance matrix (from βΣF β⊤ + Σe), and use that to calculate the minimum-variance-portfolio weights.

```{r}
# Error variance, removes covariances
S_e = diag( apply( e, 2, var ) )

# Variance of factors
S_f = cov(f)

S_model = S_e + b %*% S_f %*% t(b)
Si = solve( S_model )
w_mv_model = rowSums(Si)/sum(Si)
w_mv_model
```

## Part D
Creating the portfolio returns by multiplying the returns by the weights

sharpe ratio is the mean portfolio return minus risk free return divided by the std dev of the port returns, but risk free return is 0
```{r}
R_mv_sample = R %*% weights
R_mv_model = R %*% w_mv_model

(Sharpe_mv_sample = mean( R_mv_sample ) / sd( R_mv_sample ))
(Sharpe_mv_model = mean( R_mv_model ) / sd( R_mv_model ))
```

## Part E
```{r}
C_sample = (1+R_mv_sample) %>% cumprod()
C_model = (1+R_mv_model) %>% cumprod()
plot(C_sample, type = "l", ylim=c(1, max(C_sample, C_model)),
     ylab = "gross return", xlab = "day")
lines(C_model, col = 2)
legend( "topleft", col=c(1,2), lwd=2, legend = c("Sample covariance", "Industry factor model covariance"))
```
