---
title: "Midterm_2023"
author: "Richard Ye"
output: html_document
date: "2023-03-11"
---

# Q4

```{r}
a = 0.05
z = seq(0,100,0.01)
evar = 1/z * ( log(exp(z)-1) - log(z) - log(0.05))

which.min(evar)

plot(z[4000:7000], evar[4000:7000], type="l")

z[which.min(evar)]
```

By way of calculating the evar for z from 0 to 100 (I tested up to 1000) we can see that a value of `z=54.37` minimizes EVaR.Of course, we can make `z` more granular to get a more precise value for the optimal z.

# Q5

```{r}
library(tseries)
library(zoo)

tickers = c("^GSPC", "AAPL", "MSFT", "AMZN", "NVDA", "GOOGL", "BRK-B", "GOOG", "TSLA", "XOM", "UNH")
N = length(tickers)

P = list() # list for holding prices

for (i in 1:N) {
  # cat("Downloading ", i, " out of ", N , "\n")
  P[[i]] = get.hist.quote(instrument = tickers[i], 
    start = as.Date("2015-01-01"), 
    end=as.Date("2020-12-31"), 
    compression="d", quote = "AdjClose", 
    retclass = "zoo", quiet = T)
}
```


## Part A

```{r}
R_mut=lapply(P, FUN = function(x){ diff(x) /stats::lag(x,-1) }) # calculate MF returns
net_r = matrix(unlist(R_mut), ncol=N)
colnames(net_r) = tickers
head(net_r)
```

## Part B

```{r}
S0 = 1000

A2 = P[[2]]["2018-11-08"]
A1 = P[[2]]["2016-10-31"]

St = (A2[[1]]-A1[[1]]) * S0
St
```

## Part C

```{r, warning=FALSE}
# By our in class theory, we now the that the weighted sum of net returns are 
# still net returns (here I just divide by 2 as they are equally weighted)
aapl_xom = net_r[,c(2,10)]
rp = rowSums(aapl_xom) / 2

c_fitted = MASS::fitdistr(rp, "t")
c_fitted
```

The fitted distribution has 3.0318 degrees of freedom.

## Part D

```{r, warning=FALSE}
d_fitted = MASS::fitdistr(aapl_xom , "t")
d_fitted

sigma = d_fitted$estimate[[2]]
v = d_fitted$estimate[[3]]
var = sigma^2 * (v / (v-2))
var
```

The distribution of an equally weighted portfolio of the two stocks has mean `r d_fitted[[1]]` and variance `r var`.

## Part E

```{r}
library(quadprog)
mkt = net_r[,1]
net_r = net_r[,2:11]
COV=cov(net_r)
MU=colMeans(net_r)
SD=sqrt(diag(COV))
N=dim(net_r)[2] 

plot(SD, MU, pch=16, cex=1.2, col= 2, xlim=c(0,.1), ylim=c(-0.001,.004))
abline(v=0, lty=2); abline(h=0, lty=2) 
text(SD, MU, tickers, cex=1, pos=4)

Amat = cbind(rep(1,N),MU)
mu.p = seq( -.001, .006,length=100)
sd.p = mu.p; 

for (i in 1:length(mu.p)) {
  bvec=c(1,mu.p[i]) 
  out=quadprog::solve.QP(Dmat=2*COV,dvec=rep(0,N),Amat=Amat,bvec=bvec,meq=2)
  sd.p[i] = sqrt(out$value)
}
lines(sd.p,mu.p,type="l", lwd=2, col=2) # plot least variance portfolios

```

## Part F

```{r}
xom = net_r[,10]
mu = mean(xom)
sharpe =(mu)/sd(xom)
sharpe 

model = lm(xom ~ mkt)
beta = model$coefficients[[2]]
treynor = mu/beta
treynor

jensens = model$coefficients[[1]]
jensens
```

# Q6

## Part A

```{r}
x = runif(1000)
theta = 2
cly1 = 1/x^(theta)-1

y = runif(1000)
cly2 = 1/y^(theta)-1
plot(x, y)
```

## Part B

```{r}
x2 = qt(x, 2)
y2 = qt(y, 4)
plot(x2, y2)
```



